---
title: 'Question 1 '
documentclass: elsarticle
Thesis_FP: no
output:
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
  html_document:
    df_print: paged
Author1: Sahil Bhugwan
Ref1: "Github-https://github.com/SBhugwan "
Email1: 21075492\@sun.ac.za
CorrespAuthor_1: yes
keywords: "COVID-19"
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 12pt
linestretch: 1.5
link-citations: yes
AddTitle: yes
abstract: |
  The Covid-19 pandemic has wreaked havoc on many facets of our lives, and
  continue to affect travel, work and how people socially interact 
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(RColorBrewer)
source("/Users/sahilbhugwan/Downloads/Data science/21075492/Q1/code/Q1.R")

```

<!-- ############################## -->

<!-- # Start Writing here: -->

<!-- ############################## -->

# Introduction \label{Introduction}

COVID-19 was a unique time in the wold with basically the whole world going into a lock down. It therefore is crucial to look at how certain countries performed we we take a particular look at how Africa did compared to the rest of the world.

# Africa

This section will look at how Africa does compared to the rest of the world. It is important to note that in Africa they are more used to responding to outbreaks fro example the Ebola outbreak.

First i will be looking at the average deaths compared to other regions

```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.cap = "Average deaths \\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 6}

AVD

```

It is clear that the average deaths in Africa seem to be much lower than that to the rest of the world this suggesting that Africa might have been quicker to respond to the infection rates. However it is important to note that more people live outside of Africa. Though we could look at other important consideration, just as testing of COVID.

```{r Figure2,  warning =  FALSE, fig.align = 'center', fig.cap = "Testing rates \\label{Figure2}", fig.ext = 'png', fig.height = 5, fig.width = 6}


TP
```

This graph shows that Africa had less test on average compared to the rest of the world. This could mean that on average Africa could have had less positive case of Covid compared to the world. Which wold make intuitive sense given the fact that Africa does have less people that of the rest of the world.

## Healthcare capacity in Africa

In these section we will look in term "hospitals" in how Africa performed compared to the rest of the World. The first thing that i will look at is how many hospital beds

```{r Figure3,  warning =  FALSE, fig.align = 'center', fig.cap = "Hospital Beds \\label{Figure3}", fig.ext = 'png', fig.height = 5, fig.width = 6}

HB

```

It is clear that when COVID hit the world the number of bed needed increased dramatically however the increase was more prominent in other regions outside of Africa. The could be due to numerous reasons. A possibility could be the fact that in Africa they had less ICU patients compared to the rest of the World.

```{r Figure4,  warning =  FALSE, fig.align = 'center', fig.cap = "ICU Patients \\label{Figure4}", fig.ext = 'png', fig.height = 5, fig.width = 6}

HCC

```

It is clear that Africa didn't have such a large spike in ICU patients than the rest of the world. What we can gather from this is that Africa was handled the pandemic efficiently in that it was quick to respond to the first outbreak and was able to control the spread of it.

```{r Figure5,  warning =  FALSE, fig.align = 'center', fig.cap = "Hospitalization VS ICU Admissions  \\label{Figure5}", fig.ext = 'png', fig.height = 8, fig.width = 7}

HFvICU


```

```{r Figure6,  warning =  FALSE, fig.align = 'center', fig.cap = "Hospitalization VS ICU Admissions  \\label{Figure6}", fig.ext = 'png', fig.height = 8, fig.width = 7}

SHFICU

```

There by looking at the two graph that Africa responded much quicker that that of the rest of the world to increase its hospital facilities to cope with the increase in ICU patients.

This shows that AFrica on probabary also didnt have as many people infected or that when there was a vaccine the number of new cases to people was under control.

```{r Figure7,  warning =  FALSE, fig.align = 'center', fig.cap = " Ave cases vs vaccinated  \\label{Figure7}", fig.ext = 'png', fig.height = 8, fig.width = 7 }

MCFV

```

Therefore we can see that in Africa the proportion on new case to people vaccinated remained relatively closed togethor and didnt get out of control.

An intersting observation will be to look at the impact of the intervention.

```{r Figure8,  warning =  FALSE, fig.align = 'center', fig.cap = " Ave cases vs vaccinated  \\label{Figure8 }", fig.ext = 'png', fig.height = 8, fig.width = 6 }

SI
```

The stringency index is a composite measurebased on nine response indicators including schoolclosures, workplace closures, and travel bans. This shows how effective the interventions where with regards to controlloing the pandemic.

# Poverty levels

Next i will be looking to see if specific groups for example those in extreme poverty had it worse

```{r Figure9, warning =  FALSE, fig.align='center', fig.cap=" Extreme poverty  \\label{Figure9 }", fig.ext='png', fig.height=8, fig.width= 6, message=FALSE, warning=FALSE}

EPL

```

Next i will look at Perform analysis based on life expectancy

```{r Figure10,  warning =  FALSE, fig.align = 'center', fig.cap = "Life Expectancy \\label{Figure10}", fig.ext = 'png', fig.height = 6, fig.width = 6}
LE
```

# Conclusion
There it can be seen that Covid will have a lasting impact on the world. Though surprisingly Africa did perform a lot better than one would expect considering  that it is third world country. 