---
title: "Data Science Test"
output: github_document
date: "2023-06-16"
---

# The purpose of this README is to show my solutions to the Data science 871 exam.

The first thing i did is loadpackages that i may need 
```{r}
suppressMessages(library(tidyverse)) 
suppressMessages(library(tinytex))
suppressMessages(library(viridis))
suppressMessages(library(wordcloud))
suppressMessages(library(RColorBrewer))

```

The next thing I did was create this folder, specifically the 21075492.Rproj and corresponding folders, as well as the sub-directories for each question. These also have their own projects. Within those folders you will find, amongst other things, a) pdfs with the answers to the relevant questions, b) a code folder. 


# Question 1

This question was with regards to the COVID-19 Pandemic. I answered this question in three parts 


```{r message=FALSE, warning=FALSE}
source("/Users/sahilbhugwan/Downloads/Data science/21075492/Q1/code/Q1.R")

```

First:  i looked at how Africa countries did compared to different regions.
My thinking was i would look at the average deaths in Africa compared to Europe. This is because Africa is generally considered to be a third world country compared that to most European countries.However from the graph below it is clear that Africa had on average less deaths than Europe. 


Comparing average deaths in Africa to Europe

```{r message=FALSE, warning=FALSE}
AVD
```

Next i looked  Testing and positivity rates in Africa compared to other regions. The percent positive will be high if the number of positive tests is too high, or if the number of total tests is too low. A higher percent positive suggests higher transmission and that there are likely more people with coronavirus in the community who haven't been tested yet. 

```{r message=FALSE, warning=FALSE}
TP
```

Next i looked at healthcare capacity to ICU patients. This is because when COVID hit many hospitals couldn't keep up with the increase in ICU patients which meant they lacked the necssary equiment. 

```{r message=FALSE, warning=FALSE}
HCC
```

The second part:  i looked at to see that if a person got COVID would they be at risk. It is clear that those that the older people where more at risk. This is due to the fact that they have weaker immmune systems. 


```{r message=FALSE, warning=FALSE}
LE

```

The third part: i looked at different regions hospitalization facilities, and whether this led or lagged ICU admissions.

i decided to look at Hospitalization Facilities vs. ICU Admissions this because i wanted to see that as COVID got worse and spread more. Hospitals would have had to increase the facilities are make althernative arrangements to deal with the increased supply of sick people. 


```{r message=FALSE, warning=FALSE}
HFvICU
```

As an interesting analysis i thought i would do a stringency index. The stringency index is a measure that quantifies the strictness of government policies or regulations in response to various events or crises such as COVID-19. The stringency index takes into account a range of policy indicators, such as school closures, travel restrictions, public event cancellations, and social distancing measures, among others. By combining these indicators into a single index, it provides a measure of the overall stringency of government actions in a particular region or country.

```{r message=FALSE, warning=FALSE}
SI
```


# Question 2 

In order to challenge my friend's claim about the weather in the mid parts of England, I have decided to conduct an analysis using weather data from London. 

```{r message=FALSE, warning=FALSE}
source("/Users/sahilbhugwan/Downloads/Data science/21075492/Q2/code/Q2.R")
```

I first starting by showing the maximum temperature trend. The graph below shows where UK at heatwaves as well well as the general trend of the average temperature. 



```{r message=FALSE, warning=FALSE}
 print(MT)
```

Given that it is common knowledge that is rains a lot in the UK and from the previous graph we can see the average trend of temperatures was relatively low. I decided  to do a scatter plot for temperature vs. precipitation. (for more analysis on the precipitation i do have a graph for it in my Q2 pdf)

```{r message=FALSE, warning=FALSE}
print(TemP)
```

Next given that the temperature is always low i wanted to see on the in a year the  number of days the max temperature less than 21.1 degrees Celsius. 

```{r}
L21 
```

Lastly my friend believes that it is mostly sunny however i wanted to see how many days in the year is the temperature above 32 degrees. It is extremely rare that they have more than two days. (I do have a graph in my Q2 pdf that shows the distribution of Sun duration for the year) 

```{r}
M32

```


# Question 3 

Give that Coldplay and Metallica are one of the most famous bands over time i wanted to see the  longevity and musical progression of them 


```{r message=FALSE, warning=FALSE}
source("/Users/sahilbhugwan/Downloads/Data science/21075492/Q3/code/Q3.R")
```

I first decided to look at Coldplay in my report (in Q3 folder ) it is clear that they are most popular from 2010 onwards. 
I then decided to do a graph to show there most popular songs and which album it is from. It is clear that after 2016 that is when Coldplay hit it speak with it most popular songs. (I also have a table of there most popular song an i am aware that my table didnt come out looking nice) 


```{r}
PS(CP)
```
I then did the same for metallica, however one key difference is that metallica was more popular during 
Metallica popular songs during that late 1980s.

```{r}
PS(metallica)
```

Next i wanted to see the difference in song length (in milliseconds)

```{r}
print(DS)
```

Lastly given that they are two different bands they produce different type of music hence i decided to do a Correlation matrix based on danceability, energy, instrumentalness, liveness, loudness, speechiness & tempo

```{r}
corrplot(CMCP, method = "color") #Coldplay

corrplot::corrplot(CMM, method = "color", col = colorRampPalette(c("blue", "white", "red"))(10)) #Metallica
```





# Question 4 

my superiors at SU SU   have ambitions of launching their own streaming service, hence i will show them what works. 
(The full pdf report can be found in Q4 folder.) 

```{r message=FALSE, warning=FALSE}
source("/Users/sahilbhugwan/Downloads/Data science/21075492/Q4/code/Q4.R")
```

The first thing i did was show that netflix is haveing a decline 


```{r message=FALSE, warning=FALSE}
print(Trends) 
```

Next i look at the content on netflix and it is clear the movies dominate. Th reason for this can be because movies you can watch in "one sitting" don't need to remember what happened in previous seasons

```{r message=FALSE, warning=FALSE}
Pie 
```

I then looked at what are the most popular genres on Netflix and illustrated it using a word cloud 
```{r message=FALSE, warning=FALSE}
generate_wordcloud(genre_counts)
```

I then decided to look at which  stars appear most on Netflix  the reason for this is that if they have a lot of content it means that they are popular amongst the general public. 

```{r message=FALSE, warning=FALSE}
plot_top_names(merged_data)
```

Therefore if SU wants to launch its own streaming service it should look to produce movies that are drama or comedy based and include a high profile actor/actress. 


# Question 5 

Here i am looking at what factors i could use for AppallingDesignes to create a new app. 



```{r message=FALSE, warning=FALSE}

source("/Users/sahilbhugwan/Downloads/Data science/21075492/Q5/code/Q5.R")
```

First i will be looking at the distribution of app ratings to the number of installs(count)


```{r message=FALSE, warning=FALSE}
APR
```

I then will have to look at the number of installs(count) with regards to the age categories. It is clear that an app that is useful for everyone will be most benefical. 

```{r message=FALSE, warning=FALSE}
Ratings
```

I then looked at when apps are updated to rating this is because the world is ever changing and peoples are consistently changing and want to keep up with the latest trends. 


```{r message=FALSE, warning=FALSE}
ARLU
```

Given that people have a lot of other stuff on there phone such as music, photos it is crucial to look at app sizes. This is because people will not want to install to large apps that slow down there phone. 

```{r message=FALSE, warning=FALSE}
ARS
```

I then looks at the most popular reviews left by consumers, this is to ensure to see what feedback they have received. given that "NAN" is the most common feedback it should be vital that we can find a way to get feedback from the users this will allow us to improve the app.

```{r message=FALSE, warning=FALSE}
wordcloud(term_frequency$word, term_frequency$n, scale = c(5, 0.5), max.words = 100, random.order = FALSE,
          color = brewer.pal(8, "Set2"))
```

Lastly i looked at app sentiment of certain app. this will help us understand users feelings about why they particularly like or dislike the app's offering or service. 


```{r message=FALSE, warning=FALSE}
SDA
```

