---
title: "Data Science Test"
output: html_document
date: "2023-06-15"
---

# The purpose of this README is to show my solutions to the Data science 871 exam.

The first thing i did is loadpackages that i may need 
```{r}
suppressMessages(library(tidyverse)) 
suppressMessages(library(tinytex))
suppressMessages(library(viridis))
suppressMessages(library(wordcloud))

```





#Question 4 
What works in Streaming service if SU lauches its own one 
The full pdf report can be found in Q4 folder.

```{r}
source("/Users/sahilbhugwan/Downloads/Data science/21075492/Q4/code/Q4.R")
```

The first thing to look as is netfix decline 
```{r}
print(Trends) 
```

Next i look at the content on netflix and it is clear the movies dominate 

```{r}
Pie 
```

I then looked at what are the most popular genres on Netflix and illustrated it using a word cloud 
```{r}
generate_wordcloud(genre_counts)
```

I also looked at which stars appear most on netflix 
```{r}
plot_top_names(merged_data)
```

Therefore if SU wants to launch its own streamig service it should look to produce movies that are drama or comdey based and include a high profile actor/actress. 
