---
title: "Data Science Test"
output: html_document
date: "2023-06-15"
---

# The purpose of this README is to show my solutions to the Data science 871 exam.

The first thing i did is loadpackages that i may need 
```{r}
suppressMessages(library(tidyverse)) 
suppressMessages(library(tinytex))
suppressMessages(library(viridis))
suppressMessages(library(wordcloud))

```


#Question 2 

```{r message=FALSE, warning=FALSE}
source("/Users/sahilbhugwan/Downloads/Data science/21075492/Q2/code/Q2.R")
```
Line chart for Max tempretures over the years 

```{r message=FALSE, warning=FALSE}
 print(MT)
```

scatter plot for temperature vs. precipitation
```{r message=FALSE, warning=FALSE}
print(TemP)
```


#Question 4 
What works in Streaming service if SU lauches its own one 
The full pdf report can be found in Q4 folder.

```{r}
source("/Users/sahilbhugwan/Downloads/Data science/21075492/Q4/code/Q4.R")
```

The first thing to look as is netfix decline 
```{r}
print(Trends) 
```

Next i look at the content on netflix and it is clear the movies dominate 

```{r}
Pie 
```

I then looked at what are the most popular genres on Netflix and illustrated it using a word cloud 
```{r}
generate_wordcloud(genre_counts)
```

I also looked at which stars appear most on netflix 
```{r}
plot_top_names(merged_data)
```

Therefore if SU wants to launch its own streamig service it should look to produce movies that are drama or comdey based and include a high profile actor/actress. 


#Question 5 

Here i will be looking at app size

```{r message=FALSE, warning=FALSE}

source("/Users/sahilbhugwan/Downloads/Data science/21075492/Q5/code/Q5.R")
```


App ratings

```{r message=FALSE, warning=FALSE}
APR
```

App ratings per content

```{r message=FALSE, warning=FALSE}
Ratings
```


App rating compared to last updated

```{r message=FALSE, warning=FALSE}
ARLU
```

App Size compared to rating

```{r message=FALSE, warning=FALSE}
ARS
```

User Reviews

```{r message=FALSE, warning=FALSE}
wordcloud(term_frequency$word, term_frequency$n, scale = c(5, 0.5), max.words = 100, random.order = FALSE,
          color = brewer.pal(8, "Set2"))
```

App Sentiment
```{r message=FALSE, warning=FALSE}
SDA
```

