---
title: "Question 5 "
documentclass: elsarticle
Thesis_FP: no
output:
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
  html_document:
    df_print: paged
Author1: "Sahil Bhugwan"
Email1: "21075492\\@sun.ac.za"
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: |
  Appalling Designs pitch for a new app based on past experaince 
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
suppressMessages(library(tidyverse))

source("/Users/sahilbhugwan/Downloads/Data science/21075492/Q5/code/Q5.R")

```

<!-- ############################## -->

<!-- # Start Writing here: -->

<!-- ############################## -->

# Introduction \label{Introduction}

Using Google play and user reports to compile an analysis on there being new app for AppallingDesigns

# APPs {.unnumbered}

For the apps i will be looking at a few points


<!-- The following is a code chunk. It must have its own unique name (after the r), or no name. After the comma follows commands for R which are self-explanatory. By default, the code and messages will not be printed in your pdf, just the output: -->

```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.cap = "APP ratings  \\label{Figure1}", fig.ext = 'png', fig.height = 3, fig.width = 6}

 
APR
```

It can bee seen that apps that have a rating between 4-5 tend to have more downloads. It is also important to take note of for who the apps are for.


```{r Figure2,  warning =  FALSE, fig.align = 'center', fig.cap = "CONTENT   \\label{Figure2}", fig.ext = 'png', fig.height = 5, fig.width = 6}

Ratings

```

There is apps are for any age groups they tend to be most downloaded this is because you have a wider audience.


## App ratings 

Important considerations to look at is that apps must be contentiously updated as users want the new and best features all the time.

```{r Figure3,  warning =  FALSE, fig.align = 'center', fig.cap = "Ratings to update   \\label{Figure3}", fig.ext = 'png', fig.height = 3, fig.width = 6}

ARLU

```

therefore we can see that apps that have recently been update always tend to be downloaded. However having to update your app will also impact your clients memory on their phone.


```{r Figure4,  warning =  FALSE, fig.align = 'center', fig.cap = "Rating to Size   \\label{Figure4}", fig.ext = 'png', fig.height = 3, fig.width = 6}

ARS

```

Therefore apps need to be optimized so that they aren't to large for the users .


# User Feedback 

It is vital that we get feedback from the user to ensure that we are meeting there demands in an ever changing world.


```{r Figure5,  warning =  FALSE, fig.align = 'center', fig.cap = "User Reviews  \\label{Figure5}", fig.ext = 'png', fig.height = 3, fig.width = 6}
wordcloud(term_frequency$word, term_frequency$n, scale = c(5, 0.5), max.words = 100, random.order = FALSE,
          color = brewer.pal(8, "Set2"))
```

As we can see that the most common response is that users tend not to answer this question. It would be vital to ensure that we get feedback from them.


```{r Figure6,  warning =  FALSE, fig.align = 'center', fig.cap = "App Sentiment   \\label{Figure6}", fig.ext = 'png', fig.height = 8, fig.width = 6}

SDA

```

Looking at some of the apps it is important to ensure that users have a great opion of the app as the app can be spread through good word of mouth.



# Conclusion 

Therefore for Appalling Designs to design an app it must ensure that the app is for everyone that way it can have a bigger reach. That is regularly updated to keeps up with the changing demand, this will ensure that user will have a great sentiment towards the app.
