---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Question 4 "
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Sahil Bhugwan "  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Github- https://github.com/SBhugwan" # First Author's Affiliation
Email1: "21075492\\@sun.ac.za" # First Author's Email address

# If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.



CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 12pt                  # Set fontsize
linestretch: 1.5                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  The two longest Bands of all time Coldplay and Metallica. Comparing these two bands on longevity and musical progression 
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.height = 5,
	fig.pos = "H",
	fig.width = 6,
	message = FALSE,
	warning = FALSE
)
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

source("/Users/sahilbhugwan/Downloads/Data science/21075492/Q3/code/Q3.R")


```

<!-- ############################## -->

<!-- # Start Writing here: -->

<!-- ############################## -->

# Introduction \label{Introduction}

In this report i will be looking at the two most famous bands of all time that being coldplay and Metallica. i will be looking at a variety of analysis to come the two bands. First i will be looking at Coldplay then Metallica.

# Coldplay {.unnumbered}

The first thing is i will be looking at when coldplay become popular.

```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.cap = "Popularity of Songs \\label{Figure1}", fig.ext = 'png', fig.height = 3, fig.width = 6}

scatter_plot(CP)

```

It is clear from this that from the time coldplay came into the scene they where popular already, however during the early 2010s that is when there popularity became prominant this could be because of certain songs they released.

```{r Figure2,  warning =  FALSE, fig.align = 'center', fig.cap = "Songs over time  \\label{Figure2}", fig.ext = 'png', fig.height = 6, fig.width = 11}

PS(CP)
```

It is clear from \ref{Figure2} that they really hit there stride in the late 2010s as twice in in one album they had 3 top songs

Next looking at there correlation matrix to assess certain apsects of there music

```{r Figure3,  warning =  FALSE, fig.align = 'center', fig.cap = "Correlation matrix  \\label{Figure1}", fig.ext = 'png', fig.height = 4, fig.width = 8 }
library(corrplot)
corrplot(CMCP, method = "color")
```

# Mettallica

Next i will be looking at Mettallica. they also have been a very long perfroming band. Though it must be noted that they do perform different music to that of coldplay.

I once again will be looking at the scatter plot to see there popularity

```{r Figure4,  warning =  FALSE, fig.align = 'center', fig.cap = "Popularity of Songs \\label{Figure1}", fig.ext = 'png', fig.height = 3, fig.width = 6}

scatter_plot(metallica)

```

It is clear that mettalica where he most popular during the late 1980s. However they appeared to be less popular between 2000 and 2010 however they started gaining moment in early 2020s.

Next i will also be looking at the most popular songs

```{r Figure5,  warning =  FALSE, fig.align = 'center', fig.cap = "Songs over time  \\label{Figure5}", fig.ext = 'png', fig.height = 6, fig.width = 11}



```

It can be seen they they clearly peaked in the late 1990s

lastly i will be looking at the correlation matrix for metallica

```{r Figure6,  warning =  FALSE, fig.align = 'center', fig.cap = "Correlation matrix  \\label{Figure6}", fig.ext = 'png', fig.height = 4, fig.width = 8 }


corrplot::corrplot(CMM, method = "color", col = colorRampPalette(c("blue", "white", "red"))(10))
```

Now if we had to look at the song duration between coldplay and mettallica

```{r Figure7,  warning =  FALSE, fig.align = 'center', fig.cap = "Song Duration   \\label{Figure7}", fig.ext = 'png', fig.height = 4, fig.width = 8 }

print(DS)

```

# Extra 

Next I want to analyse the different genres i how much energy the produce

```{r Figure8,  warning =  FALSE, fig.align = 'center', fig.cap = "Engergy per Genre  \\label{Figure8}", fig.ext = 'png', fig.height = 4, fig.width = 8 }

EG(Spotify)
```

It is clear from this that metal and punk will give you the most energy
