---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Question 4 "
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Sahil Bhugwan"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Github- https://github.com/SBhugwan" # First Author's Affiliation
Email1: "21075492\\@sun.ac.za" # First Author's Email address



# Comment out below to remove both. JEL Codes only given if keywords also given.
keywords: "Netflix \\" # Use \\sep to separate


# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 12pt                  # Set fontsize
linestretch: 1.5                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  Given the age of streaming launching a new streaming serives is the way to go however questions must be asked given Netflix recent decline. This will look to see if SU Streaming should lauch its own service.  
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

source("/Users/sahilbhugwan/Downloads/Data science/21075492/Q4/code/Q4.R")

```

<!-- ############################## -->

<!-- # Start Writing here: -->

<!-- ############################## -->

# Introduction \label{Introduction}

There are multiple streaming services in the world such as Disney plus, Netflix etc. However Netflix was one of the first streaming services in the world. However the question remains has the market become to saturated given the decline in Netflix users

# Trends Over time

The first thing that i will be looking at is the content on Netflix over time

```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.cap = "Content on Netflix over time \\label{Figure1}", fig.ext = 'png', fig.height = 3, fig.width = 6}

  # This is just a random plot to show you a plot. This is done if the getwd() does not point to your Template's directory.
  # Set WD below to your project's working directory.

print(Trends) 
```

It can be see from this graph that from the late 1990s netflix really starting to take off. However from 2010 there was an explosion in the content. this lasted up an till 2015 as other streaming services started to enter the market.

# Distribution of Content

Given that Netflix is a streaming platform it offers both movies and shows

```{r Figure2, warning =  FALSE, fig.align = 'center', fig.cap = "Pie chart of content \\label{Figure2}", fig.height = 3, fig.width = 6, dev = 'png'}

Pie


```

Is is clearly evident from figure \ref{Figure2} that Netflix offers more movies than shows. To look as this more clearly we will look the bar chart to show the difference in content

```{r Figure3, warning =  FALSE, fig.align = 'center', fig.cap = "Bar graph \\label{Figure3}", fig.height = 3, fig.width = 6, dev = 'png'}

Bar
```

It is clearly evident that netflix platform hosts more movies that shows.

However one must question whether given that shows dominate on netflix how do they rate compared to shows.

```{r Figure4, warning =  FALSE, fig.align = 'center', fig.cap = "Average ratings  \\label{Figure4}", fig.height = 4, fig.width = 6, dev = 'png'}

plot_average_ratings(sorted_ratings)

```

```{r Figure5, warning =  FALSE, fig.align = 'center', fig.cap = "Age Ratings   \\label{Figure4}", fig.height = 4, fig.width = 6, dev = 'png'}

    print(certification_table)
```

# Popular people on Netflix 

If SU wants to launch its own service it should consider which actors/actress has the most content on netflix

```{r Figure6,  warning =  FALSE, fig.align = 'center', fig.cap = "Common Stars on Netflix  \\label{Figure1}", fig.ext = 'png', fig.height = 3, fig.width = 6}

plot_top_names(merged_data) 

```

Therefore Shah Rukh Khan has the most content on netflix, thus if SU has its own streaming service it should include some of his content. This is because if we look at the Figure 4.2 we can see that he has a high popularity as well as the content he is in tends to be rated above 6 on IMDb.

```{r Figure7,  warning =  FALSE, fig.align = 'center', fig.cap = "Correlation \\label{Figure3}", fig.ext = 'png', fig.height = 3, fig.width = 6}

plot_popularity("Shah Rukh Khan")

```

# Content By Country

Given that SU will be launching a streaming service in South Africa first and then branch out into the world. Given this it can be seen below that America produces the most content on netflix.

```{r Figure8,  warning =  FALSE, fig.align = 'center', fig.cap = "Content Produced by Country \\label{Figure1}", fig.ext = 'png', fig.height = 3, fig.width = 6}

plot_title_count_by_country(merged_data)

```

Therefore for SU to be unique it should potential look to produce it own unique content.

What SU could possible do is look as genres that have the most dominate genres

```{r Figure9,  warning =  FALSE, fig.align = 'center', fig.cap = "Word cloud most dominate genres \\label{Figure2}", fig.ext = 'png', fig.height = 3, fig.width = 6}

generate_wordcloud(genre_counts)

```

Therefore it can bee see that drama and comedy are the most popular content on netflix

# Conclusion
